%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Machine Learning Algorithm Engineer} % Job title
    {Tencent} % Organization
    {Oct. 2020 - Jan. 2021} % Date(s)
    {Shanghai, China} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked on an \textbf{AutoML} model optimization system designed to deliver the most optimal hyperparameters for user input data}
        \item {Implemented Hyperband and BOHB \textbf{hyperparameter opt. algo.}, improving the performance of Tencent's HPO framework by \textbf{10.9\%}}
        \item {Developed an automated hyperparameter-optimizing training module for Tencent Ti-One using \textbf{Flask} backend}
        \item {Assisted in the training of deep learning models such as ResNet \textbf{CNN} using \textbf{Tensorflow}}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Backend Developer} % Job title
    {Bilibili} % Organization
    {Jan. 2020 - May. 2020} % Date(s)
    {Shanghai, China} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Took part of Project Hawkeye, a \textbf{Java Spring}-based web scraping project monitoring all competitive products in the PVC figurine category and sales data with \textbf{MySQL} database and \textbf{Redis} cache}
        \item {Increased precision of product name matching algorithm by \textbf{14\%} using word separation analysis and one-hot encoding + cos similarity}
        \item {Developed a new scraping system using \textbf{pm2} task clustering and the \textbf{Node.js} Puppeteer library, capable of handling \textbf{8000+} requests per hour, superceding the previous one by \textbf{700\%}}
        \item {Enhanced the project's anti-scraping bypass methods using \textbf{ADSL IP proxy} rotation and building \textbf{cookies + user-agent database}}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Full-Stack Developer} % Job title
    {Ford Motor Company} % Organization
    {May. 2019 - Sep. 2019} % Date(s)
    {Waterloo, Canada} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Engaged in the Vehicle Infotainment bug report system developed in \textbf{Java Spring} and \textbf{Tomcat} server with \textbf{Knockout.js} frontend and \textbf{Splunk} database management}
        \item {Raised system user count by \textbf{20\%} by improving report processing capabilities and displaying critical information from vehicle to users}
        \item {Increased frontend report clarity and critical data awareness by executing a major overhaul to the processing system's Knockout.js UI, adding better visuals and gathering vital build information}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
